fabl: Fast Beta Linkage

### 2021-06-06 notes/fabl_wss_2.Rmd
first draft of paper

- Multiple organizations have documented casualties, and we need to find duplicates across separate datafiles to accurately estimate *documented identifiable deaths* (DID)

- Not much information, only first name, last name, and date and place of death
- Spanish language: very common for parent and child to share the same name, "second" names often omitted

>>>>

- Multiple organizations have documented casualties. El Rescate - Tutela Legal (ERTL) contains $n_A = 4420$ records, and  Salvadoran Human Rights Commission (CDHES) contains $n_B =  1323$ records.

- We need to find duplicates across separate datafiles to accurately estimate *documented identifiable deaths* (DID)

- Not much information, only first name, last name, and date and place of death

- Spanish language: very common for parent and child to share the same name, "second" names often omitted
